Enhanced Global PTM Discovery (G-PTM-D) with MetaMorpheus

### 2017-12-04 paper.tex
jdfkdjf

Correct identification of protein post-translational modifications (PTMs) is crucial to understanding many aspects of protein function in biological processes.
G-PTM-D is a recently developed technique for global identification and localization of PTMs.
Spectral file calibration prior to applying G-PTM-D, and algorithmic enhancements in the peptide database search significantly increase the accuracy, speed and scope of PTM identification.
We enhance G-PTM-D by using multi-notch searches, and demonstrate its effectiveness in identification of numerous types of PTMs, including high-mass modifications such as glycosylations.
The changes described in this work lead to a 20\% increase in the number of identified modifications and an order of magnitude decrease in search time.
The complete workflow is implemented in MetaMorpheus, a software tool which integrates the database search procedure, identification of co-isolated peptides, spectral calibration and the enhanced G-PTM-D workflow.
Multi-notch searches are also shown to be useful in contexts other than G-PTM-D, producing superior results when used instead of standard narrow-window and open database searches.
\end{abstract}

@@

%\begin{acknowledgement}

%The authors thank \ldots
%\end{acknowledgement}

>>>>

Correct identification of protein post-translational modifications (PTMs) is crucial to understanding many aspects of protein function in biological processes.
G-PTM-D is a recently developed technique for global identification and localization of PTMs.
Spectral file calibration prior to applying G-PTM-D, and algorithmic enhancements in the peptide database search significantly increase the accuracy, speed and scope of PTM identification.
We enhance G-PTM-D by using multi-notch searches, and demonstrate its effectiveness in identification of numerous types of PTMs, including high-mass modifications such as glycosylations.
The changes described in this work lead to a 20\% increase in the number of identified modifications and an order of magnitude decrease in search time.
The complete workflow is implemented in MetaMorpheus, a software tool which integrates the database search procedure, identification of co-isolated peptides, spectral calibration and the enhanced G-PTM-D workflow.
Multi-notch searches are also shown to be useful in contexts other than G-PTM-D, producing superior results when used instead of standard narrow-window and open database searches.

\end{abstract}

@@

\begin{acknowledgement}

We thank the members of the Smith lab for testing G-PTM-D and other MetaMorpheus functionality (Leah V. Schaffer, Anthony J. Cesnik, Rob Millikin, Lei Lu, Zach Rolfs, Sean Dai, Rachel Miller, Rachel Knoener), who contributed input to the improvement of mzLib, and MetaMorpheus. We thank the MetaMorpheus users outside of this lab who submitted useful comments on GitHub. This work was supported by the grant DBI-1458524 from the National Science Foundation.

\end{acknowledgement}
